%% ============================================================
%% CV — Ma, Ruiyang
%% Source of truth: ../CONTENT.md
%% To compile: pdflatex cv.tex  (run twice for correct spacing)
%% ============================================================

\documentclass[11pt, letterpaper]{article}

%% ---- Packages ----
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1in, top=0.85in, bottom=0.85in]{geometry}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{datetime2}
\usepackage{parskip}

%% ---- Hyperref config ----
\hypersetup{
  colorlinks = true,
  urlcolor   = black,
  linkcolor  = black,
  citecolor  = black
}

%% ---- Layout helpers ----
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% Column widths for dated entries (year | content)
\newcolumntype{Y}{>{\raggedleft\arraybackslash}p{1.45in}}
\newcolumntype{Z}{p{4.85in}}

%% ---- Section heading ----
\newcommand{\cvsection}[1]{%
  \vspace{10pt}%
  {\large\bfseries #1}%
  \vspace{2pt}%
  \hrule height 0.5pt%
  \vspace{6pt}%
}

%% ---- Dated entry: \entry{years}{content} ----
\newcommand{\entry}[2]{%
  \begin{tabular}{@{}YZ@{}}
    #1 & #2
  \end{tabular}%
  \vspace{3pt}%
}

%% ---- Paper entry ----
\newenvironment{paper}{%
  \vspace{2pt}%
  \begin{list}{}{%
    \setlength{\leftmargin}{0pt}%
    \setlength{\itemsep}{0pt}%
    \setlength{\parsep}{4pt}%
  }%
  \item%
}{%
  \end{list}%
  \vspace{4pt}%
}

%% ============================================================
\begin{document}
\pagestyle{plain}

%% ---- Header ----
\begin{center}
  {\LARGE\bfseries Ma, Ruiyang} \\[6pt]
  \href{mailto:rma13@illinois.edu}{rma13@illinois.edu}
  \hspace{1em}$\cdot$\hspace{1em}
  Updated: \DTMtoday
\end{center}

\vspace{4pt}

%% ---- Research Profile ----
\cvsection{Research Profile}

\begin{tabular}{@{}p{1.45in}p{4.85in}@{}}
  \textit{Research Fields} &
    Macro Finance;\enspace Monetary Economics \\[3pt]
  \textit{Research Topics} &
    Monetary Transmission;\enspace Networks;\enspace Financial Frictions;\enspace
    Identification in Macroeconomics
\end{tabular}

%% ---- Education ----
\cvsection{Education}

\entry{2023 -- Present}{%
  Ph.D. Economics, University of Illinois at Urbana-Champaign.}

\entry{2021 -- 2023}{%
  M.Sc. Policy Economy, University of Illinois at Urbana-Champaign.}

\entry{2018 -- 2020}{%
  B.A. Economics, University of Illinois at Urbana-Champaign.}

\entry{2016 -- 2018}{%
  B.S. Economics and Mathematics, Southwestern University of Finance and Economics.}

%% ---- Research ----
\cvsection{Research}

%% Paper 01
\begin{paper}
\textbf{The Financial Reallocation Channel of Monetary Policy} \hfill \textit{(in progress)}\\
with Junze Lin \\[4pt]
We embed a bank dependency network---a matrix whose entries measure the marginal
impact of one bank's fundamentals on another's market value---into a New Keynesian
model with heterogeneous households. The network generates heterogeneous bank
responses to a common policy impulse, creating a financial reallocation channel that
simultaneously stimulates aggregate demand and expands aggregate supply following an
expansionary monetary shock, reinforcing each other on output but partially offsetting
each other on inflation, thereby endogenously flattening the Phillips Curve. The
equilibrium is governed by two network objects---a credit multiplier matrix that
amplifies contemporaneous shocks and a legacy matrix that propagates the credit
distribution across time---making the effective Phillips Curve slope state-dependent
on the history of prior policy. Quantitative easing is amplified strictly more than
conventional interest-rate policy because it transmits entirely through bank balance
sheets.
\end{paper}

%% Paper 02  [hidden from website; included in CV]
\begin{paper}
\textbf{Decomposing Information Effects and Monetary Policy Shocks: An LLM Approach}
\hfill \textit{(in progress)}\\
with Jing Cynthia Wu and Shihan Xie
\end{paper}

%% Paper 03
\begin{paper}
\textbf{The Financial Reallocation Channel: How Interbank Networks Shape Spatial
Misallocation} \hfill \textit{(in progress)}\\
with Ke Gao and Hongrui Pu \\[4pt]
We propose that the topology of interbank networks shapes spatial allocative efficiency
through a financial reallocation channel. Banks with high self-amplification centrality
face greater systemic risk exposure, leading them to contract local working-capital
lending. This tighter credit supply generates endogenous microeconomic input wedges for
local firms. Using the 1863--64 National Banking Acts as an institutional shock that
rewired the network, we demonstrate that regions whose banks move to less exposed
positions experience relaxed credit constraints. Because this spatial expansion
disproportionately benefits financially constrained, inefficiently small firms, it
corrects pre-existing misallocation and boosts aggregate efficiency. Furthermore, the
layered structure of interbank claims amplifies these local credit distortions.
Ultimately, we establish that financial network architecture and trade integration
jointly determine aggregate macroeconomic productivity.
\end{paper}

%% Paper 04
\begin{paper}
\textbf{Pricing the Risk Lock-in: Financial Frictions, Endogenous Production Networks,
and Corporate Bond Spreads} \hfill \textit{(in progress)}\\
with Shaoqing Pan and Rong Yuwen \\[4pt]
This research proposes to investigate how financial frictions distort firm-level supply
chain adjustments and the resulting credit risk pricing. We develop a theoretical
framework to identify a ``risk lock-in'' mechanism, where firms facing financing
constraints and fixed adjustment costs may be unable to reconfigure their supplier
networks toward stability during periods of high uncertainty. The study examines how
these constraints break the ``flight-to-stability'' motive, potentially creating a
``volatility trap'' that depresses firm productivity, and how the market prices this
lack of flexibility, leading to a divergence in credit spreads between constrained and
unconstrained firms.
\end{paper}

%% ---- Teaching Experiences ----
\cvsection{Teaching Experiences}

\textit{University of Illinois at Urbana-Champaign}

\vspace{4pt}
\entry{FA25}{%
  Intermediate Macroeconomics (UG) \hfill Head Teaching Assistant}

\entry{SP26, SP25, FA24}{%
  Microeconomics Principles (UG) \hfill Teaching Assistant}

\entry{SP24}{%
  Macroeconomics II (PhD) \hfill Teaching Assistant}

\entry{FA23}{%
  Intermediate Macroeconomics (UG) \hfill Teaching Assistant}

%% ---- Awards and Fellowships ----
\cvsection{Awards and Fellowship}

\entry{2026}{Paul W. Boltz Fellowship, University of Illinois}

\entry{2025}{Hung-Chao and Julia Tai Family Fellowship, University of Illinois}

%% ---- Skills ----
\cvsection{Skills}

\begin{tabular}{@{}p{1.45in}p{4.85in}@{}}
  \textit{Languages} & Chinese (native), English (fluent) \\[3pt]
  \textit{Coding}    & Python, Dynare, Stata, \LaTeX
\end{tabular}

\end{document}
